On The Impact of Atoms of Confusion in JavaScript Code

### 2021-01-26 3_Method.tex
sincronizando com o GH

We posted the survey on Reddit.\footnote{Reddit is a North American online discussion platform.
Its discussion threads, often called subreddits, are sorted by subject. For our research, we po\
sted information and links to the survey in two JavaScript subreddits.} We explained our research purposes and asked developers of any level of expertise to take the survey. Within twelve hours, we collected more than 150 answers, populating more than 70 replicas of the Latin Squares. We collected significant data on time taken and discrepancies in answer correctness between confusing and non-confusing versions of the snippets. Some inconsistencies arose while building the squares, for instance, when a user quit in the middle of the survey. When this happened, the corresponding row in the square was left incomplete. We considered all squares that contained incomplete rows to be invalid during data analysis and discarded them. Since we had\
 a large enough number of samples, the squares we had to discard did not impact our analysis.

@@

\subsubsection{Participants Selection} We invited the participants of the interviews using a snow balling technique. That is, starting from our network of contacts, we invited an initial set of candidates to take part of our survey. From this initial list, we asked for indication of additional candidates. Our main criterion of selection was that all participants shoukd havebeen working professionally with JavaScript. We invited a total of 17 developers, and 15 of these agreed to participate. We conducted the interviews during a period of two weeks.

@@

After filtering out JavaScript project candidates, in the second step we built a curate dataset comprising the top \minedprojects repositories. Examples of projects in this dataset include \textsc{React}, \textsc{Node JS}, and \textsc{AngularJS}. Table~\ref{tab:projects-statistics} presents some statistics about the projects we consider in our research. The size of the projects range from small ones (5543 lines of code) to complex systems with more than 1 MLOC. All projects in our dataset have at least \num{1244} forks and \num{23672} stars. We automated all the steps to filter, clone, and collect the statistics from the repositories using Python scripts.

In the third step we mined atoms of confusion from the repositories in our curate dataset, using source code queries that we had written using the CodeQL language~\cite{moor:gttse2007}. CodeQL is an object-oriented variant of the Datalog language~\cite{rodriguez2020efficient}, and currently supports researchers and practitioners to query the source code of systems written in different languages (such as Java and JavaScript). We also automate the process o
f running the queries and exporting the results to a format that simplifies our
analysis (and also the reproduction of this study). In the final step we carry
out basic descriptive statistics, in order to understand how often the
atoms of confusion appear in practice.

>>>>

We posted the survey on Reddit.\footnote{Reddit is a North American online discussion platform.
Its discussion threads, often called subreddits, are sorted by subject. For our research, we posted information and links to the survey in two JavaScript subreddits.} We explained our research purposes and asked developers of any level of expertise to take the survey. Within twelve hours, we collected more than 150 answers, populating more than 70 replicas of the Latin Squares. We collected significant data on time taken and discrepancies in answer correctness between confusing and non-confusing versions of the snippets. Some inconsistencies arose while building the squares, for instance, when a user quit in the middle of the survey. When this happened, the corresponding row in the square was left incomplete. We considered all squares that contained incomplete rows to be invalid during data analysis and discarded them. Since we had\
 a large enough number of samples, the squares we had to discard did not impact our analysis.

@@

\subsubsection{Participants Selection} We invited the participants of the interviews using a snow balling technique. That is, starting from our network of contacts, we invited an initial set of candidates to take part of our survey. From this initial list, we asked for indication of additional candidates. Our main criterion of selection was that all participants should have been working professionally with JavaScript. We invited a total of 17 developers, and 15 of these agreed to participate. We conducted the interviews during a period of two weeks.

@@

After filtering out JavaScript project candidates, in the second step we built a curated dataset comprising the top \minedprojects repositories. Examples of projects in this dataset include \textsc{React}, \textsc{Node JS}, and \textsc{AngularJS}. Table~\ref{tab:projects-statistics} presents some statistics about the projects we consider in our research. The size of the projects range from small ones (5543 lines of code) to complex systems with more than 1 MLOC. All projects in our dataset have at least \num{1244} forks and \num{23672} stars. We automated all the steps to filter, clone, and collect the statistics from the repositories using Python scripts.

In the third step we mined atoms of confusion from the repositories in our curate dataset, using source code queries that we had written using the CodeQL language~\cite{moor:gttse2007}. CodeQL is an object-oriented variant of the Datalog language~\cite{rodriguez2020efficient}, and currently supports researchers and practitioners to query the source code of systems written in different languages (such as Java and JavaScript). We also automate the process of running the queries and exporting the results to a format that simplifies our
analysis (and also the reproduction of this study). In the final step we carry
out basic descriptive statistics, in order to understand how often the
atoms of confusion appear in practice.

### 2021-01-26 4_Result.tex
sincronizando com o GH

Figure~\ref{fig:xp} shows that more than a half of the participants hold either a BS degree or had taken some university course, meaning the participants have had some level of formal education on programming. No subject reported to have never attended university. Our audience comprises skilful developers, and 93\% of the respondents have more than one year of experience with programming (see Figure~\ref{fig:xp}). Actually, 56\% of the participants have either between four and ten years of experience (37\%) or more than ten years of experience (19\%). Other 37\% of the respondents have between one and four years of experience. In this way, we characterize the effect of atoms of confusion in JavaScript code taking into account the perceptions of both novice and experience developers.

>>>>

Figure~\ref{fig:xp} shows that more than a half of the participants hold either a BS degree or had taken some university course, meaning the participants have had some level of formal education on programming. No subject reported to have never attended university. Our audience comprises skillful developers, and 93\% of the respondents have more than one year of experience with programming (see Figure~\ref{fig:xp}). Actually, 56\% of the participants have either between four and ten years of experience (37\%) or more than ten years of experience (19\%). Other 37\% of the respondents have between one and four years of experience. In this way, we characterize the effect of atoms of confusion in JavaScript code taking into account the perceptions of both novice and experience developers.
